A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2015-03-17 paper/methodology.tex
MCMC and Dust attenuation

\subsection{MCMC}
We used a Markov Chain Monte Carlo method to find the best parameters and its 
uncertainties over each one of the boxes and each observational dataset.

Observational data set to fit is selected.
A halo catalog of a cubic box of length 250 Mpc h-1 is selected.
Initial parameters are introduced.

An UV luminosity is given to each halo as function of his mass according to equation
 \ref{eqn:luminosity}.
Luminosity is converted to magnitude using:
  \[ M_{UV} = 51.82 - 2.5 \log_{10}(L_{UV}). \]
If we consider the dust attenuation im the equation \ref{eqn. dust attenuation} we have
a dust-corrected UV Luminosity Function.

@@

Once having the LF, we compare our LF against observed LF. Our likelihood estimator is 
the sum of the square difference over each bin, divided by the number of degrees of 
freedom. We worked on the logarithmic space of luminosities to have a good fitting on
six decades.

\[ \chi^2  = \sum_{i=o}^{n}\left( x_{i,obs} - x_{i,fit} \right)^2 \]

\[ \mathcal{L} \propto \exp \left( \frac{\chi ^2}{n} \right) \]

Then we have a small variation on the parameters, it gives us a new LF and a new 
likelihood estimator $\chi^2$.

We compare the new fitting versus the old fitting.

Some restrictions where imposed over two parameters to guarantee convergence in the 
MCMC method: $0 \leq \alpha \leq 1.8 $  and $\gamma \geq 0$.

%MCMC, maximum likelihood.

%Python, Ipython Notebook, Scipy, Matplotlib, Numpy. Astropy
Finally, the UV luminosity for each galaxy can be directly related with SFR according 
to \citet{madau98}.
This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{kennicutt98}.
The relation between UV luminosity and Star Formation Rate \citep{madau98,kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

>>>>

\subsection{MCMC}
We used a Markov Chain Monte Carlo method to find the best parameters and its 
uncertainties over each one of the boxes and each observational dataset. The code was written
on Python using the Scipy, Numpy and Matplotlib libraries.

First of all, one of the four observational data sets (Bouwens, Finkelstein, Willow and McLure) 
is selected to be the model to fit.
From the whole simulated halo catalog, a subsample with cubic box shape of 
 $250\textrm{Mpc h}^{-1}$ length is selected.

With an initial set of parameters $(\alpha, \gamma, M_0,$ and $ L_0)$ the UV luminosity
for the halo is calculated as function of his mass according to equation
 \ref{eqn:luminosity}. Then Luminosity is converted to magnitude units using:
  \[ M_{UV} = 51.82 - 2.5 \log_{10}(L_{UV}). \]
If we consider the dust attenuation im the equation \ref{eqn. dust attenuation} we have
a dust-corrected UV Luminosity Function.

@@

Once having the LF, we compare our LF against observed LF. The error function we consider
is the sum of the square difference over each bin, divided by the observational data uncertain.
\[ \chi^2  = \sum_{i=o}^{n} \frac {\left( x_{i,obs} - x_{i,fit} \right)^2 }{2\sigma_i^2}\]
We worked on the logarithmic space of luminosities to have a good fitting on
six decades.

The likelihood will have this property:
\[ \mathcal{L} \propto \exp \left(  -\frac{\chi ^2}{n} \right) \], where $n$ is the number of degrees
of freedom. We have the maximum likelihood when the error is the minimum.

Each MCMC step will have have a small variation of the parameters, the UV luminosity and magnitude are 
calculated again for each halo, we have a new error $\chi_{new}^2$ and a new likelihood 
$ \mathcal{L}_{new} $.

Following the Metropolis method, we compare the new and the old likelihood:
\[ R =\frac{ \mathcal{L}_{new}  }{ \mathcal{L}_{old} }  = 
exp( \chi_{new}^2 - \chi_{old}^2 )
\]

If $  R \geq 1$, then we immediate accept the new set of parameters and start the next MCMC step.

Else, we have a chance to keep the new set. When $ R < 1$, we compare with a uniformly 
random number $p$ in the range $[0,1]$. if $ R>p$ we accept the new set of parameters and start
the next MCMC step. 
Else we reject the new set and start again with the old set.

We performed 10.000 effective MCMC steps, plus 1.000 thermalization steps over each box.
We repeated for the same box without consider dust attenuation.

Then we perform the same method over the 64 boxes and the resting three data sets.

The restrictions imposed over the parameters where $0 \leq \alpha \leq 2.0 $  and 
$\gamma \geq 0$.

Finally, the UV luminosity for each galaxy can be directly related with SFR according 
to \citet{madau98}.
This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{kennicutt98}.
The relation between UV luminosity and Star Formation Rate \citep{madau98,kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}
